% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% SIMPLE-RESUME-CV
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode,draftmode]{resume}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Kurt C. Jacobson}
\newcommand{\CVTitle}{{\today} Kurt Jacobson's Resume}
\newcommand{\CVNote}{Résumé compiled on {\today}}

% Web address to use in tile
\newcommand{\CVWebpage}{www.kcjengr.com}

% E-mail to use in title
\newcommand{\CVEmail}{Kurt.C.Jacobson@gmail.com}
% \newcommand{\CVEmail}{kcjengr@gmail.com}
% \newcommand{\CVEmail}{kurt@kcjengr.com}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={KCJ's Résumé},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={Résumé, CV},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/2521+Flair+Knoll+Ct+NE,+Atlanta,+GA+30345}
{2521 Flair Knoll Ct., Atlanta, Georgia 30345, USA}
\par
\href{mailto:\CVEmail}
{\CVEmail}
\,\SubBulletSymbol\,
(505)\,303-1933
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{http://www.kennesaw.edu/}
{\textbf{Kennesaw State University}},
Marietta, Georgia, USA

\Gap
\BulletItem
B.S. in
\href{http://engineering.kennesaw.edu/engineering-technology/}
{Mechanical Engineering Technology}
\hfill
\DatestampYM{2013}{08} --
\DatestampYM{2016}{12}
\begin{Detail}
\SubBulletItem
Cumulative GPA: 4.0 / 4.0
\SubBulletItem
Focus:
Manufacturing, Engineering Graphics

\SubBulletItem
Minor:
\href{http://engineering.kennesaw.edu/nuclear-studies/}
{Nuclear Engineering}
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\Entry
\href{http://engineering.kennesaw.edu/nuclear-studies/}
{\textbf{Center for Nuclear Studies}},
Kennesaw State University

\Gap
\BulletItem
Undergraduate Research Project
\hfill
\DatestampYMD{2016}{06}{1} --
\DatestampYMD{2017}{04}{7}
\begin{Detail}
\SubBulletItem
Project:
Alpha Radiation Detector Development And Testing Under Various Conditions
\SubBulletItem
Supervisors:
Dr. Eduardo B. Farfan and
Dr. Sandip Das
\SubBulletItem
Focus:
Development of a precise and low-cost Chang-Rosenblum type alpha particle detector.
\SubBulletItem
Presented at the National Conference on Undergraduate Research, University of Memphis, Apr 6-8, 2017
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:WorkExperience}

\Entry
\href{http://kennesaw.edu/}
{\textbf{Kennesaw State University}},
Marietta, Georgia, USA

\Gap
\BulletItem
Laboratory Manager,
KSU Center for Nuclear Studies
\hfill
\DatestampYM{2015}{12} --
\DatestampYM{2017}{4}
\begin{Detail}
\SubBulletItem
Managed liquid nitrogen supply for nuclear lab, including ordering and coordinating delivery.
\SubBulletItem
Maintained five state-of-the-art radiation detectors and all associated equipment.
\SubBulletItem
Tracked usage and maintained inventory of more then 25 radiation sources.
\SubBulletItem
Coordinated and ran 4-8 undergraduate reactor simulation labs per semester (Spring, Summer, Fall).
\end{Detail}

\Gap
\BulletItem
Student Assistant,
KSU Department of Mechanical Engineering
\hfill
\DatestampYM{2016}{1} --
\DatestampYM{2016}{12}
\begin{Detail}
\SubBulletItem
Graded all homework and tests for multiple upper level Mechanical and Nuclear Engineering courses.
\SubBulletItem
Presented and promoted the Nuclear Engineering lab on multiple occasions to industry and university boards.
\SubBulletItem
Set up equipment and assisted instructors in running the Radiation Detection and Measurement labs.
\end{Detail}

\Gap
\BulletItem
Supplemental Instruction Leader,
Southern Polytechnic College of Engineering
\hfill
\DatestampYM{2015}{8} --
\DatestampYM{2016}{12}
\begin{Detail}
\SubBulletItem
Pioneered use of Supplemental Instruction (SI) for upper level engineering courses at KSU.
\SubBulletItem
Compiled worksheets and developed and maintained a website to aid in distributing materials to students.
\SubBulletItem
Enhanced student engagement, improved grades, and reduced attrition rate within the Strength of Materials course.
\end{Detail}


\BigGap
\Entry
\href{http://tubularfab.com}
{\textbf{Tubular Fabrication LLC}},
Flowery Branch, Georgia, USA

\Gap
\BulletItem
Lead Mechanical Engineer
\hfill
\DatestampYM{2015}{5} --
\DatestampYM{2015}{8}
\begin{Detail}
\SubBulletItem
Developed a novel, semi-automatic, pneumatically actuated, precision large-bore chuck.
\SubBulletItem
Created dedicated, easy to use, interactive software for calculating cut path trajectory.
\SubBulletItem
Fabricated a functional prototype and tested in production environment.
\SubBulletItem
Achieved significantly increased accuracy of notches, and reduced cycle times by more than 75\%.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\BulletItem
President's List,
Fall 2013 through Fall 2016,
Kennesaw State University
\hfill
\DatestampY{2013} --
\DatestampY{2016}
\begin{Detail}
\Item
Awarded each semester for maintaining an overall GPA of 4.0.
\end{Detail}

\Gap
\BulletItem
Clarence Arnston Award,
KSU Mechanical Engineering Technology Department
\hfill
\DatestampYMD{2016}{12}{15}
\begin{Detail}
\Item
Awarded for Outstanding Senior in Mechanical Engineering Technology in the year 2016.
\end{Detail}

\Gap
\BulletItem
Engineering Technology Student of the Year,
Georgia Engineering Alliance
\hfill
\DatestampYMD{2016}{2}{13}
\begin{Detail}
\Item
Awarded at the Georgia Engineers Week Awards Gala.
\end{Detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Affiliations\newline
\& Activities}
{Professional Affiliations \& Activities}
{PDF:ProfessionalAffiliationsActivities}

%\Gap
\BulletItem
\href{http://www.ans.org/}
{American Nuclear Society},
Professional Member
\hfill
\DatestampYM{2017}{2} -- Present

%\Gap
\BulletItem
\href{https://owllife.kennesaw.edu/organization/KNS}
{Kennesaw Nuclear Society},
Vice Present
\hfill
\DatestampYM{2016}{1} -- \DatestampYM{2016}{12}

%\Gap
\BulletItem
\href{http://www.sme.org/}
{Society of Manufacturing Engineers},
Student Member
\hfill
\DatestampY{2016} -- Present

%\Gap
\BulletItem
\href{http://www.asme.org/}
{American Society of Mechanical Engineers},
Student Member
\hfill
\DatestampYM{2015}{10} -- Present


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL CERTIFICATIONS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Professional Certifications}
{Professional Certifications}
{PDF:ProfessionalCertifications}

%\Gap
\BulletItem
\href{http://www.sme.org/cmfgt/}
{Certified Manufacturing Technologist},
Society of Manufacturing Engineers
\hfill
\DatestampYM{2016}{12} --
\DatestampYM{2019}{12}

%\Gap
\BulletItem
\href{http://www.solidworks.com/sw/support/mcad-certification-programs.htm}
{Certified SolidWorks Associate},
DS SolidWorks Corporation
\hfill
\DatestampYM{2014}{11} --
\DatestampYM{2018}{1}


%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
SolidWorks, Fusion360, SolveSpace, HSMWorks,
Python, Bash, C/C++, MATLAB, GTK+, Qt,
reStructuredText, HTML, MarkDown, AsciiDoc, \LaTeX,
Microsoft Office.


%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests \& Hobbies}
{Interests \& Hobbies}
{PDF:InterestsHobbies}

\Entry
Precision Machining,
Industrial Automation,
Open Source Software Development,
Linux,
Vintage Automobiles,
Pattern Making, Metal Casting,
Woodworking, Hiking.

\end{Body}

\end{document}
